Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-01 paper.qmd
Added langevitour for true model of the toy example

```{r}
#| label: best-fit-two-curvy-proj-tsne

@@

## First projection
model_prj1 <- cbind(
  c(0.37847,-0.06517,0.04231,0.01655),
  c(-0.06466,-0.27052,0.22131,-0.15235))

>>>>

```{r}
#| label: prep-data-for-proj-tsne-best

@@

```{r}
#| eval: false
df_model_data_two_curvy_filtered <- bind_rows(true_model_two_curvy, data_two_curvy)

langevitour::langevitour(df_model_data_two_curvy_filtered[1:(length(df_model_data_two_curvy_filtered)-1)],
                         lineFrom = wireframe_true_model$from,
                         lineTo = wireframe_true_model$to,
                         group = factor(df_model_data_two_curvy_filtered$type,
                                        c("data", "true model")),
                         levelColors = c(clr_choice, "#000000"))
```

```{r}
#| label: best-fit-two-curvy-proj-tsne
## First projection
model_prj1 <- cbind(
  c(0.37847,-0.06517,0.04231,0.01655),
  c(-0.06466,-0.27052,0.22131,-0.15235))
